### 2018-08-22 Sections/cryptowars.tex
Some new stubs
Dephasing dist metric
Minor touch ups
qkd hacking draft0

In the case of RSA encryption, whose security derives from the believed computational hardness of factorising large numbers, the most efficient known classical algorithm for integer factorisation is the general number field sieve (GNFS)\index{General number field sieve}, with time-complexity,
\begin{align} \label{eq:GNFS_scaling}
	O(\exp [O(1) (\log n)^{\frac{1}{3}} (\log\log n)^{\frac{2}{3}}]),
\end{align}
which scales poorly for large $n$, keeping in mind that present-day implementations of RSA accommodate key lengths of up to 4,096 bits, as for example is implemented by the Pretty Good Privacy (PGP)\index{Pretty Good Privacy (PGP)} package.

@@

In the case of RSA public-key cryptography the attack is more direct -- with access to a scalable quantum computer, Shor's algorithm\index{Shor's algorithm} can be employed to efficiently factorise large integers, allowing private keys to be retrieved from public keys. Unlike the brute-force attacks, which yielded only a quadratic enhancement, Shor's algorithm is exponentially faster than the classical GNFS, requiring runtime of only,
\begin{align}
	O([\log n]^2[\log\log n][\log\log\log n]).
\end{align}
Compare this with the classical case given in Eq.~(\ref{eq:GNFS_scaling}).

@@

@@

@@

\comment{Attacks based on bad implementation rather than bad theory}

>>>>

In the case of RSA encryption, whose security derives from the believed computational hardness of factorising large numbers, the most efficient known classical algorithm for integer factorisation is the general number field sieve (GNFS)\index{General number field sieve}, with time-complexity,
\begin{align} \label{eq:GNFS_scaling}
	O(\exp (O(1) (\log n)^{\frac{1}{3}} (\log\log n)^{\frac{2}{3}})),
\end{align}
which scales poorly for large $n$, keeping in mind that present-day implementations of RSA accommodate key lengths of up to 4,096 bits, as for example is implemented by the Pretty Good Privacy (PGP)\index{Pretty Good Privacy (PGP)} package.

@@

In the case of RSA public-key cryptography the attack is more direct -- with access to a scalable quantum computer, Shor's algorithm\index{Shor's algorithm} can be employed to efficiently factorise large integers, allowing private keys to be retrieved from public keys. Unlike the brute-force attacks, which yielded only a quadratic enhancement, Shor's algorithm is exponentially faster than the classical GNFS, requiring runtime of only,
\begin{align}
	O((\log n)^2(\log\log n)(\log\log\log n)).
\end{align}
Compare this with the classical case given in Eq.~(\ref{eq:GNFS_scaling}).

@@

%
% Quantum Enigma machines
%

\subsection{Quantum Enigma machines}\index{Quantum Enigma machines}

@@

%
% Quantum Secret Sharing
%

\subsection{Quantum secret sharing}\index{Quantum secret sharing}

@@

\comment{To do}
Hacking attacks are related to the weaknesses of an implementation. A first common feature of hacking attacks is that they are feasible, or almost feasible, with present-day technology. 
\subsection{Trojan horse attack}
The best-known example is the family of Trojan horse attacks, in which Eve probes the settings of Alice’s and/or Bob’s devices by sending some light into them and collecting the reflected signal. 
Actually, the first kind of hacking attack that was considered is a form of Trojan horse that would come for free: it was noticed that some photon counters  silicon-based avalanche photodiodes  emit some light at various wavelengths when they detect a photon  Kurtsiefer et al., 2001 . If this light carries some information about which detector has fired, it must be prevented from propagating out, where Eve could detect it.

\subsection{Photon number splitting attack}
\comment{Attacks based on bad implementation rather than bad theory}
